### 2019-04-01 thesis-template/msc-thesis.tex
add thesis tree

Tensor Field Visualization is gaining importance as a relevant tool for the analysis of fluid and solid mechanics. Tensors are found most commonly in medical, scientific and engineering applications. A tensor is a $n$-D generalization of a matrix and appears e.g. as Jacobi-Matrix in Flow Fields or as stress tensor in solid continuum mechanics. Basically, tensors describe stretchings, rotations and volume changes in both solid and fluid material. While most techniques focus on symmetric tensor field visualization (like Glyphs and Tensor Field Lines), some other recent works adress the problem of asymmetric tensor field visualization. The issue with asymmetric or antisymmetric tensors is that they do not always yield real eigenvalues, which is needed to determine an eigenbasis to set up glyphs, hyperstreamlines or tensor field lines. \cite{pang&zheng} et.al. proposed the concept of dual eigenvectors and \cite{zhang} eigenvector manifold and eigenvalue manifold to visualize eigenvectors in the complex domain. The concept of Tensor Magnitude has been introduced by \cite{laramee} for means of physical interpretation and proposed an efficient glyph and hyperstreamline hybrid approach, which made dynamic interaction in real-time in 2D tensor fields feasible.\\

\begin{figure}[h]
  \centering
 {
    \includegraphics[width=0.6\textwidth]
    {img/hyperstreamlines.png}
  }
  \caption{Cauchy-Spannungstensor}
  \label{Skalierung}
\end{figure}
Worum geht es? Beispiel(e)! Illustrationen sind hier meist sinnvoll
zum Verständnis. Warum ist das Thema wichtig? In welchem Kontext?

\section{Objectives}

Implement a FTLE-related approach in tensor field visualization (both symmetric and asymmetric) for detecting ridges/LCS.
Visualize oriented deformation glyphs
In diesem Abschnitt sollen neben den Herausforderungen und der
Problemstellung insbesondere die Ziele der Arbeit beschrieben werden.

@@

\textbf{Symmetric Tensor Field Visualization}\\
\cite{pang&zheng} et.al. proposed a texture-based visualization approach called HyperLIC, which extends the concept of LIC to symmetric tensor fields by using an anisotropic 2D-filter kernel oriented along the major/minor eigenvectors. The notion of tensor field topology and the concept of Hyperstreamlines was first introduced by \cite{delmarcelle&hesselink}. The placement of tensor field lines as hyperstreamlines was recently improved by \cite{spencer} et.al. for glyph packing. \cite{feng} et. al. used Voronoi Tesselation for placing the glyphs. Superquadric glyphs have been proposed by \cite{Schultz&Kindlmann} for better flexibility for non-positive definite tensors. \cite{deleeuw&vanwijk} visualize the partial derivative gradient, the Jacobian of the tensor field.
\\
\textbf{Asymmetric Tensor Field Visualization}\\
\cite{pang&zheng}
Typischerweise im letzten Abschnitt dieses Kapitels wird dann auf
verwandte Arbeiten eingegangen. Entsprechende Arbeiten sind geeignet
zu zitieren. Beispiel: Die wurde erstmalig in den Arbeiten von Spitz
und Gertz \cite{Spitz2016a} gezeigt \ldots Details dazu werden in
dem Buch von Newman zu Netzwerken \cite{Newman2010} erläutert \ldots.

>>>>

Tensor Field Visualization is gaining importance as a relevant tool for the analysis of fluid and solid mechanics. Tensors are found most commonly in medical, scientific and engineering applications. A tensor is a $n$-D generalization of a matrix and appears e.g. as Jacobi-Matrix in Flow Fields or as stress tensor in solid continuum mechanics. Basically, tensors describe stretchings, rotations and volume changes in both solid and fluid material. While most techniques focus on symmetric tensor field visualization (like Glyphs and Tensor Field Lines), some other recent works adress the problem of asymmetric tensor field visualization. The issue with asymmetric or antisymmetric tensors is that they do not always yield real eigenvalues, which is needed to determine an eigenbasis to set up glyphs, hyperstreamlines or tensor field lines. \cite{pang&zheng} et.al. proposed the concept of dual eigenvectors and \cite{zhang} extended it to pseudo-eigenvectors and introduced eigenvector and eigenvalue manifold to visualize eigenvectors in the complex domain. The concept of Tensor Magnitude has been introduced by \cite{laramee2} for means of physical interpretation. They also proposed an efficient glyph and hyperstreamline hybrid approach, which made dynamic interaction in real-time in 2D tensor fields feasible.\\

\begin{figure}[h]
  \centering
 {
    \includegraphics[width=0.6\textwidth]
    {img/hyperstreamlines.png}
  }
  \caption{Hyperstreamlines in Tensor Field Visualization}
  \label{Skalierung}
\end{figure}
Worum geht es? Beispiel(e)! Illustrationen sind hier meist sinnvoll
zum Verständnis. Warum ist das Thema wichtig? In welchem Kontext?

\section{Objectives}
The problem setting encomprises the visualization of tensor fields, i.e. mostly 2D/3D-grids consisting of mainly second-order tensors (cnf. Cauchy-Stress Tensor). The main purpose of visualization in general is to reduce or encode some set of numbers in some readable, explorable and more intuitive representation. This implies e.g. clustering, structuring or projection techniques. The objective of this work is to implement a FTLE-related approach in tensor field visualization (both symmetric and asymmetric) for detecting ridges/LCS (Lagrangian Coherent Structures). These structures can be identified as repelling, attracting and saddling (forming a saddle) local features, which frequently represent key structures in nature. The real part of the eigenvalues is exploited for sign change (contractions/tensions) which leads to the concept of deformation glyphs w. attached arrows pointing inward/outward for the two types of normal stresses. Practically, in its eigenbasis there are no shear stresses existent for the stress tensor just the principal normal stresses.

In diesem Abschnitt sollen neben den Herausforderungen und der
Problemstellung insbesondere die Ziele der Arbeit beschrieben werden.

@@

\textbf{Symmetric Tensor Field Visualization}\\
\cite{pang&zheng} et.al. proposed a texture-based visualization approach called HyperLIC, which extends the concept of LIC to symmetric tensor fields by using an anisotropic 2D-filter kernel oriented along the major/minor eigenvectors. The notion of tensor field topology and the concept of Hyperstreamlines was first introduced by \cite{delmarcelle&hesselink}. The placement of tensor field lines as hyperstreamlines was recently improved by \cite{spencer} et.al. for glyph packing. A good overview of seeding strategies is given by \cite{mcloughlin}. \cite{feng} et. al. used Voronoi Tesselation for placing the glyphs. Superquadric glyphs have been proposed by \cite{Schultz&Kindlmann} for general (non-positive definite) tensors. \cite{deleeuw&vanwijk} visualize the partial derivative gradient, the Jacobian of the tensor field to sense the local properties of the field. 
\\
\textbf{Asymmetric Tensor Field Visualization}\\
\cite{pang&zheng} et.al. proposed the concept of dual eigenvectors and \cite{zhang} extended it to pseudo-eigenvectors and introduced the eigenvector/eigenvalue manifolds to visualize eigenvectors in the complex domain. \cite{laramee} et.al. focused on the efficient implementation and visualization of these structures and provided an interactive visualization system for asymmetric tensors applicable in fluid and solid dynamics. In this work, we will use the singular vectors yielded from singular value decomposition to avoid complex values yielded from eigenvalue decomposition. This will allow us to set up glyphs representing the major/minor axis of the underlying transformation for every kind of (asymmetric/symmetric) tensor. We will then use global-illumination techniques to take it one step further and to generate a flow map, permitting us to compute an FTLE-like field on the tensor fields. 
\\

Typischerweise im letzten Abschnitt dieses Kapitels wird dann auf
verwandte Arbeiten eingegangen. Entsprechende Arbeiten sind geeignet
zu zitieren. Beispiel: Die wurde erstmalig in den Arbeiten von Spitz
und Gertz \cite{Spitz2016a} gezeigt \ldots Details dazu werden in
dem Buch von Newman zu Netzwerken \cite{Newman2010} erläutert \ldots.
